Dynein project log

### 2016-12-26 thesis_stuff/thesis_stuff.tex
Add parameter finding run log to thesis_stuff.tex with progress of runs.

\begin{align*}
  \frac 12 c_b \Delta \theta_{ba} = \Delta G_{bind, high} &\rightarrow c_b = 2\Delta G_{bind, high} \approx 140 \mbox{ kJ/mol}\\
\end{align*}

\subsection{ATP Concentration from Weihong's Paper}
Weihong says in the Supplemental Methods section that the ATP concentration of the ``dynein motility buffer'' used to take his videos was 1mM, with no added ADP or Pi.

>>>>

\begin{align*}
  \frac 12 c_b \Delta \theta_{ba}^2 = \Delta G_{bind, high} &\rightarrow c_b = 2\Delta G_{bind, high} \approx 140 \mbox{ kJ/mol}\\
\end{align*}

\subsection{ATP Concentration from Weihong's Paper}
Weihong says in the Supplemental Methods section that the ATP concentration of the ``dynein motility buffer'' used to take his videos was 1mM, with no added ADP or Pi.\\

\subsection{Parameter fitting}
Lots of different manual simulations and their outcomes.

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l | l | p{3cm} | p{5cm} |}
    \hline
    Ls & Lt & kb & kub & cm & cb & ct & notes & outcome\\\hline
    22.1 & 11.1 & 5000 & 5000 & 23.0 & 0.23 & 0.23 & trying to find good springs for binding & unbinding probability is about $10^{-150}$, spring constants too high to allow unbinding\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & trying to find good springs for binding & unbinding probability oscillates around $10^{-9}$, seems good will explore more\\\hline
  \end{tabular}
\end{center}
